Type Classes for Mathematics in Type Theory

### 2010-06-30 jar.tex
Back to 'multiplication/division by 2.

Other examples of operations on natural numbers that are sensible choices for specialization include: subtraction, distance, binary division and multiplication.

>>>>

Other examples of operations on natural numbers that are sensible choices for specialization include: subtraction, distance, and division and multiplication by 2.
